### 2024-03-29 paper.tex

    \includegraphics[width=0.55\textwidth, trim={0 0 0 0},clip]{author_files/14-bis.jpeg}

@@

      \includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{author_files/nimbodetector.png}	

@@

      \includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{author_files/sensor.png}	

@@

    \includegraphics[width=0.85\textwidth, trim={0 0 0 0},clip]{author_files/graph.png}

@@

  \lstinputlisting[caption=Foobar source code, label={lst:listing-f90}, language=Fortran]{foobar.f90}

>>>>

    \includegraphics[bb=0 0 2632 1814, width=0.55\textwidth, trim={0 0 0 0},clip]{author_files/14-bis.jpeg}

@@

      \includegraphics[bb=0 0 1024 1024, width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{author_files/nimbodetector.png}	

@@

      \includegraphics[bb=0 0 1024 1024, width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{author_files/sensor.png}	

@@

    \includegraphics[bb=0 0 700 524, width=0.85\textwidth, trim={0 0 0 0},clip]{author_files/graph.png}

@@

  \lstinputlisting[caption=Foobar source code, label={lst:listing-f90}, language=Fortran]{author_files/foobar.f90}
